---
title: "Dev Submission"
output:
  html_document:
    df_print: paged
---

Step 1: Installing necessary package 
```{r}
#install.packages("Benchmarking")
library("Benchmarking")
```



Step 2: Reading input
```{r}
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2,1.2,0.7), ncol=2)

y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000), ncol=2)

colnames(x) <- c("staff Hours Per Day","Supplies Per Day")

colnames(y) <- c("Reimbursed Patient Days","Privately Paid Patient Days")

x

y

```


Step 3: Running DEA Analysis for FDH
```{r}
fdh <- dea(x,y,RTS="fdh") 

peers(fdh) 

lambda(fdh) 

dea.plot.isoquant(x,y,RTS="fdh") 

summary(fdh)

```

Step 4: Running DEA Analysis for CRS
```{r}
crs <- dea(x,y,RTS = "crs") 

peers(crs) 

lambda(crs) 

dea.plot.isoquant(x,y,RTS="crs") 

summary(crs)

```

Step 5: Running DEA Analysis for VRS
```{r}
vrs <- dea(x,y,RTS = "vrs") 

peers(vrs) 

lambda(vrs) 

dea.plot.isoquant(x,y,RTS="vrs") 

summary(vrs)

```

Step 6: Running DEA Analysis for IRS
```{r}
irs <- dea(x,y,RTS = "irs") 

peers(irs) 

lambda(irs) 

dea.plot.isoquant(x,y,RTS="irs") 

summary(irs)

```

Step 7: Running DEA Analysis for DRS
```{r}
drs <- dea(x,y,RTS = "drs") 

peers(drs) 

lambda(drs) 

dea.plot.isoquant(x,y,RTS="drs") 

summary(drs)


```

Step 7: Running DEA Analysis for FDH+
```{r}
fdh_plus <- dea(x,y,RTS="fdh+") 

peers(fdh_plus) 

lambda(fdh_plus) 

summary(fdh_plus)

dea.plot(x,y,RTS="fdh",ORIENTATION="in-out",txt=LETTERS[1:length(x)])
dea.plot(x,y,RTS="add",ORIENTATION="in-out",add=TRUE,lty="dashed",lwd=2)
dea.plot(x,y,RTS="fdh+",ORIENTATION="in-out",add=TRUE,lty="dotted",lwd=3,col="red")

```


Step 8: Compare & Contrast


FDH technology and input orientated efficiency
Number of firms with efficiency==1 are 6 out of 6 
Mean efficiency: 1 
---                
  Eff range      #   %
        E ==1    6 100



VRS technology and input orientated efficiency
Number of firms with efficiency==1 are 5 out of 6 
Mean efficiency: 0.983 
---                
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     0  0
        E ==1    5 83



DRS technology and input orientated efficiency
Number of firms with efficiency==1 are 4 out of 6 
Mean efficiency: 0.974 
---                
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     1 17
        E ==1    4 67



CRS technology and input orientated efficiency
Number of firms with efficiency==1 are 4 out of 6 
Mean efficiency: 0.974 
---                
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     1 17
        E ==1    4 67
_


IRS technology and input orientated efficiency
Number of firms with efficiency==1 are 5 out of 6 
Mean efficiency: 0.983 
---                
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     0  0
        E ==1    5 83
_


FDH+ technology and input orientated efficiency
Number of firms with efficiency==1 are 6 out of 6 
Mean efficiency: 1 
---                
  Eff range      #   %
        E ==1    6 100
 